# Reproducible Research: Peer Assessment 1
```{r echo=FALSE}
options(scipen=1, digits=2)
```

***
## Loading and preprocessing the data
```{r}
# Read csv data from local zip file.
act = read.csv(unz("activity.zip", "activity.csv"))
# Format the interval time to a four-digit number string.
act$interval = formatC(act$interval, width=4, flag="0")
# Convert strings in "date"" column to date objects.
act$date = as.Date(as.character(act$date))
```

***
## What is mean total number of steps taken per day?
```{r}
# Get subset of complete cases.
act.cc = act[complete.cases(act),]
# Sum each days total steps.
act.cc.sum = sapply(split(act.cc$steps, act.cc$date), sum)
# Display histogram of total steps per day.
hist(act.cc.sum, breaks=10,
     main="Histogram of total steps per day over two months",
     xlab="Total steps per day")
# Calculate the mean and median
act.mean = mean(act.cc.sum)
act.median = median(act.cc.sum)
```
#### The *mean* and *median* total number of steps taken per day are `r act.mean` and `r act.median` respectively.


***
## What is the average daily activity pattern?
```{r}
act.cc.ave = sapply(split(act.cc$steps, act.cc$interval), mean)
plot(act.cc.ave, type = "l", xaxt="n", 
     main="Average number of steps\nacross two months for each five-minute interval",
     ylab="Average total steps",
     xlab="Five-minute intervals from 0000 to 2400")
# Place 2-hour ticks along x-axis.
axis(1, at=seq(0, length(act.cc.ave), by=24), labels=formatC(seq(0,2400,by=200), width=4, flag="0"), las=2)
act.cc.ave.max = which.max(act.cc.ave)
abline(v=act.cc.ave.max, col="red", lty=2)
text(act.cc.ave.max, act.cc.ave[act.cc.ave.max], paste(act.cc.ave[act.cc.ave.max], names(act.cc.ave.max), sep=" @ "), pos=4)
```

***
## Imputing missing values


***
## Are there differences in activity patterns between weekdays and weekends?
