# Reproducible Research: Peer Assessment 1
```{r echo=FALSE}
options(scipen=1, digits=2)
```

***
## Loading and preprocessing the data
```{r}
# Read csv data from local zip file.
act = read.csv(unz("activity.zip", "activity.csv"))
# Convert strings in "date"" column to date objects.
act$date = as.Date(as.character(act$date))
```

***
## What is mean total number of steps taken per day?
```{r}
# Get subset of complete cases.
act.cc = act[complete.cases(act),]
# Sum each days total steps.
act.cc.sum = sapply(split(act.cc$steps, act.cc$date), sum)
# Display histogram of total steps per day.
xlab = "Total steps per day"
hist(act.cc.sum, breaks=10, xlab=xlab, main=paste("Histogram of", tolower(xlab)))
# Calculate the mean and median
act.mean = mean(act.cc.sum)
act.median = median(act.cc.sum)
```
#### The mean and median total number of steps taken per day are `r act.mean` and `r act.median` respectively.


***
## What is the average daily activity pattern?


***
## Imputing missing values


***
## Are there differences in activity patterns between weekdays and weekends?
